\documentclass[11pt,A4]{IGAA2018_Abstract}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\thispagestyle{empty}

\title{Fast Divergence-Conforming Reduced Basis Methods for steady Navier-Stokes Flow}

\author{
  Eivind Fonn$^{*}$, Harald v.~Brummelen$^{\dagger}$,
  Trond Kvamsdal$^{\mathsection\ddagger}$, Adil Rasheed$^{\mathsection}$,
  Muhammad S.~Siddiqui$^{\ddagger}$
}

\address{$^{\mathsection}$ Department of Applied Mathematics and Cybernetics\\
SINTEF Digital\\
PO Box 4760, 7465 Trondheim, Norway\\
$^{*}$ e-mail: eivind.fonn@sintef.no, web page: http://www.sintef.no
\and
$^{\dagger}$ Department of Mechanical Engineering\\
Eindhoven University of Technology\\
PO Box 513, 5600 MB Eindhoven, The Netherlands
\and
$^{\ddagger}$ Department of Mathematical Sciences\\
Norwegian University of Science and Technology\\
Institutt for Matematiske Fag, NTNU, 7491 Trondheim, Norway}

\begin{document}

Numerical methods and tools for simulating flow around complex
geomeries have evolved rapidly in recent years. However, their usage
usually requires access to high-performance computing facilities,
which is not always feasible. New methods are required for an
ever-increasing demand for computationally efficient desktop tools
usable in real-time control, optimization and management. One such
solution is dimensionality reduction through Reduced Order Modelling
(ROM) based on Proper Orthogonal Decomposition
(POD).\cite{Quarteroni2016rbm}

We detail in this work an experiment involving two-dimensional
stationary flow around a NACA0015 airfoil at various velocities and
angles of attack. Two different methods are proposed: a
run-of-the-mill reduced basis method based on a conventional
Taylor-Hood high-fidelity solver, and one based on a
divergence-conforming isogeometric flow solver. The reduced bases were
constructed with POD and enhanced with
supremizers\cite{Ballarin2015ssp} to stabilize the pressure field. We
show how the latter method produces a fully divergence-free reduced
basis, and how this property influences the linear systems by creating
three-by-three block triangular matrices, a structure that can be
exploited for significant speedups over the traditional matrix
structure arising from the regular method.

\begin{thebibliography}{99}
  \bibitem{Quarteroni2016rbm} A.~Quarteroni, A.~Manzoni, and F.~Negri,
    “Reduced Basis Methods for Partial Differential Equations”,
    \textit{Springer International Publishing}, 1st Edition (2016).
  \bibitem{Ballarin2015ssp} F.~Ballarin, A.~Manzoni, A.~Quarteroni,
    and G.~Rozza, “Supremizer stabilization of POD-Galerkin
    approximation of parametrized steady incompressible Navier Stokes
    equations”, \textit{Int.~J.~Numer.~Meth.~Engng.},
    Vol.~\textbf{102}, pp.~1136--1161 (20125).
\end{thebibliography}

\end{document}
